Understanding the impacts of video-guided activities on parent-child interaction

### 2020-04-08 paper/manuscript.tex
fixed a couple NAs and line 328 issue, and improved appendix

\shorttitle{Impacts of videos on parent-child interaction}
\affiliation{
\vspace{0.5cm}
\textsuperscript{1} Department of Psychology, Stanford University\\\textsuperscript{2} Gallaudet University\\\textsuperscript{3} Cornell University}
\keywords{digital parenting advice; joint attention; lexical diversity; guided play\newline\indent Word count: 5056}
\usepackage{csquotes}
\usepackage{upgreek}
\captionsetup{font=singlespacing,justification=justified}

@@

This theory of change is typically grounded in ideas about guided play and early language stimulation.
Child-directed speech varies not only in quantity (i.e., the number of total tokens), but also in quality in terms of the diversity of the tokens (Malvern, Richards, Chipere, \& Durán, 2004) or the context-appropriateness of the speech (Cartmill et al., 2013), both of which have been linked to children's subsequent language development.
Further, language learning -- especially the acquisition of early vocabulary in the first years -- appears to be supported preferentially by parents and children \emph{jointly attending} to some object or activity (Baldwin, 1991; Bigelow, MacLean, \& Proctor, 2004).
Episodes of joint attention are frequent during guided play, when parents set goals and scaffold their child's activities (Weisberg, Hirsh-Pasek, \& Golinkoff, 2013; Wood, Bruner, \& Ross, 1976).
Thus, the current literature supports interventions that encourage parents to provide high-quality language and interaction through something like guided play -- whether via reading books or playing with a shape-sorter at home, or via a conversation about categories in the supermarket.

@@

A second coder independently coded a third of the videos (i.e., 20 of the 60 videos, approximately equally distributed across ages) to establish reliability.
The two coders had a reliability of ICC = 0.79 with 95\% confidence interval (CI) = {[}0.55, 0.91{]} for rate of parent bids for JA (number of bids per minute); ICC = 0.34 with 95\% CI = {[}-0.11, 0.67{]} for rate of passive JA episodes (per minute); ICC = 0.66 with 95\% CI = {[}0.32, 0.85{]} for rate of coordinated JA episodes; ICC = 0.33 with 95\% CI = {[}-0.11, 0.67{]} for rate (seconds per minute) of passive JA episodes, and ICC = 0.60 with 95\% CI = {[}0.24, 0.82{]} for rate (seconds per minute) of coordinated JA episodes.

@@

For each transcript of child-directed speech, the caregivers' unique word \emph{types} and \emph{tokens} (total words) uttered were tallied and converted to rates (e.g., tokens per minute of play), and the type-token ratio (TTR) was calculated as a measure of lexical diversity.
Although we initially preregistered TTR as our measure of lexical diversity (since it is a simple, commonly used measure), it has been noted that TTR is correlated with the length of a text, which has led to the development of new measures such as the measure of textual lexical diversity (MTLD; McCarthy \& Jarvis, 2010).
Thus, we also measure lexical diversity with MTLD, which is calculated as the mean length of sequential word strings in a text that maintain a given TTR value (here we use the value proposed by McCarthy \& Jarvis (2010): 0.720).

We fit a Bayesian mixed-effects linear regression predicting TTR as a function of condition, age (centered), and their interaction with a random intercept per video using rstanarm (Goodrich, Gabry, Ali, \& Brilleman, 2018).
For effects that are at least 95\% likely to be non-zero according to the posterior distribution (i.e., probability of direction: \emph{pd}; Makowski et al. (2019a)), we report estimated coefficients (\(\beta\)) as well as 89\% Bayesian credible intervals (89\% CI)\footnote{89\% CIs are recommended for Bayesian analyses because unless the effective sample size (ESS) is on the order of 10,000, the 95\% credible interval is unstable (Kruschke, 2014; Makowski et al., 2019b; McElreath, 2018). Our ESS ranges from 2,000-5,000, and thus we report the tighter, more stable interval.}, demarcating the range within which 89\% of the posterior falls, meaning that given the observed data, the effect has 89\% probability of falling within this range (see Appendix for more an illustrated explanation).
There was lower TTR in the Activity Video condition (mean: 0.32) than in the No Video condition (mean: 0.43, \(\beta=\)-0.11, 89\% CI = {[}-0.15, -0.07{]}, \emph{pd} = 1).
A similar regression instead predicting MTLD also found lower lexical diversity in the Activity Video condition (mean MTLD: 17.87) than in the No Video condition (mean: 27.09, \(\beta=\)-9.24, 89\% CI = {[}-14.07, -4.21{]}, \emph{pd} = 1{]}), with no notable influence of age.
Figure \ref{fig:lexdiv} (top) shows the mean of each lexical diversity measure (TTR and MTLD) by condition.

@@

We also fit Bayesian mixed-effects linear regression models predicting each of the above lexical diversity and joint attention dependent variables as a function of fixed effects of condition, age (centered), the child's sex, parent's education level, and the subscales of the EPAQ: Early Learning (EL), Affection and Attachment (AA), and Rules and Respect (RR), along with interactions of condition and EL, AA, and RR.
These models included random intercepts per video.
Of these exploratory regressions, two showed notable effects involving the EPAQ subscales, and one other showed an effect of the child's sex.
First, in the word types regression, parents with higher Affection and Attachment scores used more word types per minute after watching an Activity Video (interaction of condition and AA: \(\beta=6.81\), 89\% CI = {[}0.87, 13.13{]}, \emph{pd} = 0.97).
Second, in the regression examining the rate of passive JA episodes, parents scoring higher on the Rules and Respect (RR) subscale had a lower rate of passive JA episodes (\(\beta=-0.34\), 89\% CI = {[}-0.62, -0.07{]}, \emph{pd} = 0.98).
However, higher RR parents who saw an Activity Video did not show this decrease in passive JA (interaction of condition and RR: \(\beta=0.63\), 89\% CI = {[}0.23, 1.03{]}, \emph{pd} = 0.99).
This regression also found that more educated parents showed a lower rate of passive JA episodes (\(\beta=-0.25\), 89\% CI = {[}-0.45, -0.04{]}, \emph{pd} = 0.97).
Finally, parents made bids for JA at a higher rate with male children than with female children (male mean: 2.76 bids/min, female mean: 2.49, \(\beta=0.82\) 89\% CI = {[}0.06, 1.54{]}, \emph{pd} = 0.96).

@@

84 infants (F = 36, M = 46) aged 12-24 months
(20 12-17.9 month-olds in the Activity Video condition;
21 12-17.9 month-olds in the Science Video condition;
22 18-24 month-olds in the Activity Video condition;
21 18-24 month-olds in the Science Video condition) and their parents participated in the same museum as Experiment 1.
We included infants who were exposed to English at least 75 percent of the time or who were exposed less but whose participating parent reported that they primarily speak English with their child at home.
Forty-nine percent of participants (n = 41) had been exposed to two or more languages as indicated by their parent.
Parents identified their children as White (n = 39), Asian (n = 20), African American/Black (n = 1), Biracial (n = 9), other (n = 7), or declined to state (n = 8).
Sixteen parents reported their child was of Hispanic origin.
Parents tended to be highly-educated, with reports of highest level of education ranging from some college (n = 2), four-year college (n = 36), some graduate school (n = NA), to completed graduate school (n = NA) or declined to state (n = 13).

@@

The procedure for Experiment 2 matched that of Experiment 1, except that parents in the Control Video condition watched a control video before the play session.
Consistent with the No-Video control condition in Experiment 1, parents in the Control Video condition were told to play with their child as they would at home, and were not given additional instructions.
The coding procedure also matched that of Experiment 1.
To establish reliability a second coder independently coded 25 of the 84 videos, approximately equally distributed across ages.
The two coders had a reliability of ICC = 0.81 with 95\% confidence interval (CI) = {[}0.62,0.91{]} for number of parent bids for JA; ICC = 0.74 with 95\% CI = {[}0.48, 0.88{]} for number of passive JA episodes; ICC = 0.80 with 95\% CI = {[}0.61, 0.91{]} for number of coordinated JA episodes; ICC = 0.72 with 95\% CI = {[}0.44, 0.86{]} for total duration of passive JA episodes, and ICC = 0.88 with 95\% CI = {[}0.75, 0.94{]} for total duration of coordinated JA episodes.

@@

Parents' child-directed speech during the play sessions (mean duration: 3.08 min) was transcribed and processed, and bids and episodes of joint attention were coded according to the same procedure used in Experiment 1.
We first report preregistered regressions\footnote{Although the preregistration implied the use of standard linear mixed-effects regression through the specification of adopting an alpha level of .005 for statistical significance, the non-convergence of some of the below regressions led us to switch to Bayesian regression. Using a Bayesian analysis also has the added benefit of not requiring arbitrary decisions about changing alpha levels to attempt to correct for multiple comparisons (Gelman, 2008).} predicting TTR and rate of word tokens, as well as an exploratory regression predicting MTLD.
We then turn to preregistered regressions of parental bids for joint attention and the total number of JA episodes.

@@

We fit a Bayesian mixed-effects linear regression predicting TTR as a function of age (centered) and condition with an interaction term, and with random intercepts per video.
This revealed lower TTR after the Activity Video (mean: 0.38) than after the Science Video (mean: 0.48, \(\beta=-0.09\), , 89\% CI = {[}-0.14, -0.05{]}, \emph{pd} = 1).
The preregistered regression predicting the number of tokens used by parents revealed no effects.
An exploratory mixed-effects linear regression predicting MTLD found no effect of age or condition.
Figure \ref{fig:lexdiv} (bottom left and middle) shows the mean of each lexical diversity measure (TTR and MTLD) by condition.
Regressions with the same structure predicting the number of words tokens found no effect of age or condition.
The means of the lexical measures are shown in Table \ref{e2tab}.

\begin{table}

\caption{\label{tab:e2tab}\label{e2tab} Lexical diversity measures in Experiment 2.}
\centering
\begin{tabular}[t]{l|r|r|r|r|r|r|r|r}
\hline
Condition & TTR (M) & (sd) & MTLD (M) & (sd) & Types (M) & (sd) & Tokens (M) & (sd)\\
\hline
Science Video & 0.48 & 0.08 & 22.45 & 10.57 & 28.05 & 8.54 & 61.85 & 23.58\\
\hline
Activity Video & 0.38 & 0.12 & 20.63 & 8.66 & 26.57 & 8.39 & 77.22 & 32.09\\
\hline
\end{tabular}
\end{table}

@@

We fit Bayesian mixed-effects linear regressions predicting the rate of parental bids for joint attention and the rate of JA episodes as a function of fixed effects of condition, age (centered), and their interaction, with random intercepts per video.
Shown in Figure \ref{fig:JA} (left bottom), parents made bids for JA at a greater rate after watching the Activity Video (mean: 4.23, 95\% conf. int.: {[}3.85, 4.65{]}; \(\beta=1.05\), 89\% CI = {[}0.53, 1.58{]}, \emph{pd} = 1)) than after the Science Video (mean: 3.19, 95\% conf. int.: {[}2.83, 3.57{]}).
There were no other effects on parental bids for JA.

The regression predicting rate of JA episodes revealed an effect of condition (\(\beta=0.51\), e2tjaCond, with JA episodes occurring at a greater rate after the Activity Video (mean: 2.88, 95\% conf. int.: {[}2.61, 3.17{]}) than after the Control Video (mean: 2.36, 95\% conf. int.: {[}2.12, 2.60{]}).
Older children also participated in JA episodes at a lesser rate than younger children (\(\beta=-1.57\), 89\% CI = {[}-2.42, -0.65{]}, \emph{pd} = 1).
However, this age effect was moderated in the Activity Video condition (\(\beta=1.69\), 89\% CI = {[}0.34, 2.98{]}, \emph{pd} = 0.98): shown in Figure \ref{fig:JA} (right bottom), older children did not engage in episodes of JA at a lower rate after an activity video.

@@

Four additional exploratory regressions with a similar structure were carried out to predict the number and duration of coordinated and passive JA episodes.
The regression predicting the rate of coordinated JA episodes found an effect of condition (\(\beta=0.46\), 89\% CI = {[}0.13, 0.77{]}, \emph{pd} = 0.99), with a greater rate of coordinated JA episodes occurring after the Activity Video (mean: 2.19, 95\% CI: {[}1.93, 2.46{]}) than after the Control Video (mean: 1.72, 95\% CI: {[}1.52, 1.93{]}).
There was an interaction of age and condition (\(\beta=1.59\), 89\% CI = {[}0.35, 2.94{]}, \emph{pd} = 0.98), shown in Figure \ref{fig:e2ja-coord}, revealing that after an Activity Video older children participated in coordinated JA episodes at a greater rate than children in the Control Video condition.
The regression predicting the time spent in coordinated JA episodes found no notable effects.

Older children both engaged in episodes of passive JA at a greater rate with their caregiver (\(\beta=-0.89\), 89\% CI = {[}-1.54, -0.2{]}, \emph{pd} = 0.98), and spent more time in passive JA with their caregiver (\(\beta=-5.92\), 89\% CI = {[}-9.85, -1.83{]}, \emph{pd} = 0.99).
Overall, these results show that the older children in our sample engage in more and longer episodes of joint attention with their caregivers, and that activity videos in particular lead to more episodes of coordinated JA.

As for Experiment 1, we conducted a corpus characteristic analysis to examine differences parents' language use in the two conditions.
The words that were strongly indicative of being from the Activity Video condition include \enquote{big}, \enquote{little}, \enquote{give}, \enquote{small}, \enquote{cow}, \enquote{yellow}, \enquote{take}, and \enquote{put}, while words that were most characteristic of the Science Video condition include \enquote{beep}, \enquote{like}, \enquote{neigh}, \enquote{uhoh}, \enquote{say}, \enquote{for}, \enquote{does}, and \enquote{did}.

@@

This work was supported by a gift and a contract from Kinedu, Inc.~to the Language and Cognition Lab.
Thanks to members of the Language and Cognition Lab at Stanford for helpful discussion.

>>>>

\shorttitle{Impacts of videos on parent-child interaction}
\affiliation{
\vspace{0.5cm}
\textsuperscript{1} Department of Psychology, Stanford University\\\textsuperscript{2} Gallaudet University\\\textsuperscript{3} Cornell University}
\keywords{digital parenting advice; joint attention; lexical diversity; guided play\newline\indent Word count: 4995}
\usepackage{csquotes}
\usepackage{upgreek}
\captionsetup{font=singlespacing,justification=justified}

@@

This theory of change is typically grounded in ideas about guided play and early language stimulation.
Child-directed speech varies not only in quantity (i.e., the number of total tokens), but also in quality in terms of the diversity of the tokens (Malvern, Richards, Chipere, \& Durán, 2004) or the context-appropriateness of the speech (Cartmill et al., 2013), both of which have been linked to children's subsequent language development.
Further, language learning---especially the acquisition of early vocabulary in the first years---appears to be supported preferentially by parents and children \emph{jointly attending} to some object or activity (Baldwin, 1991; Bigelow, MacLean, \& Proctor, 2004).
Episodes of joint attention are frequent during guided play, when parents set goals and scaffold their child's activities (Weisberg, Hirsh-Pasek, \& Golinkoff, 2013; Wood, Bruner, \& Ross, 1976).
Thus, the current literature supports interventions that encourage parents to provide high-quality language and interaction through something like guided play---whether via reading books or playing with a shape-sorter at home, or via a conversation about categories in the supermarket.

@@

A second coder independently coded a third of the videos (i.e., 20 of the 60 videos, approximately equally distributed across ages) to establish reliability.
The two coders had a reliability of ICC = 0.79 with 95\% confidence interval (CI) = {[}0.55, 0.91{]} for rate of parent bids for JA (number of bids per minute); ICC = 0.34 with 95\% CI = {[}-0.11, 0.67{]} for rate of passive JA episodes (per minute); ICC = 0.66 with 95\% CI = {[}0.32, 0.85{]} for rate of coordinated JA episodes; ICC = 0.33 with 95\% CI = {[}-0.11, 0.67{]} for time spent (seconds per minute) in passive JA episodes, and ICC = 0.60 with 95\% CI = {[}0.24, 0.82{]} for time spent in coordinated JA episodes.

@@

For each transcript of child-directed speech, the caregivers' unique word \emph{types} and \emph{tokens} (total words) uttered were tallied and converted to rates (e.g., tokens per minute of play), and the type-token ratio (TTR) was calculated as a measure of lexical diversity.
Although we initially preregistered TTR as our measure of lexical diversity (since it is a simple, commonly used measure), it has been noted that TTR is correlated with the length of a text, which has led to the development of new measures such as the measure of textual lexical diversity (MTLD; McCarthy \& Jarvis, 2010).
Thus, we also measure lexical diversity with MTLD, which is calculated as the mean length of sequential word strings in a text that maintain a given TTR value (we use 0.72, as proposed by McCarthy \& Jarvis).

We fit a Bayesian mixed-effects linear regression predicting TTR as a function of condition, age (centered), and their interaction with a random intercept per video using rstanarm (Goodrich, Gabry, Ali, \& Brilleman, 2018).
For effects that are at least 95\% likely to be non-zero according to the posterior distribution (i.e., probability of direction: \emph{pd}; Makowski et al. (2019a)), we report estimated coefficients (\(\beta\)) as well as 89\% Bayesian credible intervals (89\% CI)\footnote{89\% CIs are recommended for Bayesian analyses because unless the effective sample size (ESS) is on the order of 10,000, the 95\% credible interval is unstable (Kruschke, 2014; Makowski et al., 2019b; McElreath, 2018). Our ESS ranges from 2,000-5,000, and thus we report the tighter, more stable interval.}, demarcating the range within which 89\% of the posterior falls, meaning that given the observed data, the effect has 89\% probability of falling within this range (see Appendix for more an illustrated explanation).
There was lower TTR in the Activity Video condition (mean: 0.32) than in the No Video condition (mean: 0.43, \(\beta=\)-0.11, 89\% CI = {[}-0.15, -0.07{]}, \emph{pd} = 1).
A similar regression instead predicting MTLD also found lower lexical diversity in the Activity Video condition (mean MTLD: 17.87) than in the No Video condition (mean: 27.09, \(\beta=\)-9.24, 89\% CI = {[}-14.07, -4.21{]}, \emph{pd} = 1), with no notable influence of age.
Figure \ref{fig:lexdiv} (top) shows the mean of each lexical diversity measure (TTR and MTLD) by condition.

@@

We also fit Bayesian mixed-effects linear regression models predicting each of the above lexical diversity and joint attention dependent variables as a function of fixed effects of condition, age (centered), the child's sex, parent's education level, and the subscales of the EPAQ: Early Learning (EL), Affection and Attachment (AA), and Rules and Respect (RR), along with interactions of condition and EL, AA, and RR.
These models included random intercepts per video.
Of these exploratory regressions, two showed notable effects involving the EPAQ subscales, and one other showed an effect of the child's sex.
First, in the word types regression, parents with higher Affection and Attachment scores used more word types per minute after watching an Activity Video (interaction of condition and AA: \(\beta=6.81\), 89\% CI = {[}0.87, 13.13{]}, \emph{pd} = 0.97).
Second, in the regression examining the rate of passive JA episodes, parents scoring higher on the Rules and Respect (RR) subscale had a lower rate of passive JA episodes (\(\beta=-0.34\), 89\% CI = {[}-0.62, -0.07{]}, \emph{pd} = 0.98).
However, after an Activity Video, higher RR parents did not show this decrease in passive JA (interaction of condition and RR: \(\beta=0.63\), 89\% CI = {[}0.23, 1.03{]}, \emph{pd} = 0.99).
Parents with higher education also showed a lower rate of passive JA episodes (\(\beta=-0.25\), 89\% CI = {[}-0.45, -0.04{]}, \emph{pd} = 0.97).
Finally, parents with male children made bids for JA at a higher rate (mean: 2.76 bids/min) than those with female children (mean: 2.49, \(\beta=0.82\), 89\% CI = {[}0.06, 1.54{]}, \emph{pd} = 0.96).

@@

84 infants (F = 36, M = 46) aged 12-24 months
(20 12-17.9 month-olds in the Activity Video condition;
21 12-17.9 month-olds in the Science Video condition;
22 18-24 month-olds in the Activity Video condition;
21 18-24 month-olds in the Science Video condition) and their parents participated in the same museum as Experiment 1.
We included infants who were exposed to English at least 75 percent of the time or who were exposed less but whose participating parent reported that they primarily speak English with their child at home.
Forty-nine percent of participants (n = 41) had been exposed to two or more languages as indicated by their parent.
Parents identified their children as White (n = 39), Asian (n = 20), African American/Black (n = 1), Biracial (n = 9), other (n = 7), or declined to state (n = 8).
Sixteen parents reported their child was of Hispanic origin.
Parents tended to be highly-educated, with reports of highest level of education ranging from some college (n = 5), four-year college (n = 28), some graduate school (n = 2), to completed graduate school (n = 36) or declined to state (n = 13).

@@

The procedure for Experiment 2 matched that of Experiment 1, except that parents in the Control Video condition watched a control video before the play session.
Consistent with the No-Video control condition in Experiment 1, parents in the Control Video condition were told to play with their child as they would at home, and were not given additional instructions.
The coding procedure also matched that of Experiment 1.
To establish reliability a second coder independently coded 25 of the 84 videos, approximately equally distributed across ages.
The two coders had a reliability of ICC = 0.81 with 95\% confidence interval (CI) = {[}0.62,0.91{]} for number of parent bids for JA; ICC = 0.74 with 95\% CI = {[}0.48, 0.88{]} for number of passive JA episodes; ICC = 0.80 with 95\% CI = {[}0.61, 0.91{]} for number of coordinated JA episodes; ICC = 0.72 with 95\% CI = {[}0.44, 0.86{]} for time spent (secs/min) in passive JA episodes, and ICC = 0.88 with 95\% CI = {[}0.75, 0.94{]} for time spent in coordinated JA episodes.

@@

Parents' child-directed speech during the play sessions (mean duration: 3.08 min) was transcribed and processed, and bids and episodes of joint attention were coded according to the same procedure used in Experiment 1.
We first report preregistered regressions\footnote{Although the preregistration implied the use of standard linear mixed-effects regression through the specification of adopting an alpha level of .005 for statistical significance, the non-convergence of some regressions led us to switch to Bayesian regression. Using a Bayesian analysis has the added benefit of not requiring arbitrary changes to alpha levels to correct for multiple comparisons (Gelman, 2008).} predicting TTR and rate of word tokens, as well as an exploratory regression predicting MTLD.
We then turn to preregistered regressions of parental bids for joint attention and the total number of JA episodes.

@@

We fit a Bayesian mixed-effects linear regression predicting TTR as a function of age (centered) and condition with an interaction term, and with random intercepts per video.
This revealed lower TTR after the Activity Video (mean: 0.38) than after the Science Video (mean: 0.48, \(\beta=-0.09\), , 89\% CI = {[}-0.14, -0.05{]}, \emph{pd} = 1).
The preregistered regression predicting the number of tokens used by parents revealed no effects.
An exploratory mixed-effects linear regression predicting MTLD found no effect of age or condition.
Figure \ref{fig:lexdiv} (bottom left and middle) shows the mean of each lexical diversity measure (TTR and MTLD) by condition.
Regressions with the same structure predicting the number of words tokens found no effect of age or condition.
The means of the lexical measures are shown in Table 1.

\begin{table}[tbp]
\begin{center}
\begin{threeparttable}
\caption{\label{tab:e2tab}Mean lexical diversity measures in Experiment 2.}
\begin{tabular}{lllllllll}
\toprule
Condition & \multicolumn{1}{c}{TTR} & \multicolumn{1}{c}{(sd)} & \multicolumn{1}{c}{MTLD} & \multicolumn{1}{c}{(sd)} & \multicolumn{1}{c}{Types} & \multicolumn{1}{c}{(sd)} & \multicolumn{1}{c}{Tokens} & \multicolumn{1}{c}{(sd)}\\
\midrule
Science Video & 0.48 & 0.08 & 22.45 & 10.57 & 28.05 & 8.54 & 61.85 & 23.58\\
Activity Video & 0.38 & 0.12 & 20.63 & 8.66 & 26.57 & 8.39 & 77.22 & 32.09\\
\bottomrule
\end{tabular}
\end{threeparttable}
\end{center}
\end{table}

@@

We fit Bayesian mixed-effects linear regressions predicting the rate of parental bids for joint attention and the rate of JA episodes as a function of fixed effects of condition, age (centered), and their interaction, with random intercepts per video.
Shown in Figure \ref{fig:JA} (left bottom), parents made bids for JA at a greater rate after watching the Activity Video (mean: 4.23, 95\% conf. int.: {[}3.85, 4.65{]}; \(\beta=1.05\), 89\% CI = {[}0.53, 1.58{]}, \emph{pd} = 1) than after the Science Video (mean: 3.19, 95\% conf. int.: {[}2.83, 3.57{]}).
There were no other effects on parental bids for JA.

The regression predicting rate of JA episodes revealed an effect of condition (\(\beta=0.51\), 89\% CI = {[}0.18, 0.84{]}, \emph{pd} = 0.99), with JA episodes occurring at a greater rate after the Activity Video (mean: 2.88, 95\% conf. int.: {[}2.61, 3.17{]}) than after the Control Video (mean: 2.36, 95\% conf. int.: {[}2.12, 2.60{]}).
Older children also participated in JA episodes at a lesser rate than younger children (\(\beta=-1.57\), 89\% CI = {[}-2.42, -0.65{]}, \emph{pd} = 1).
However, this age effect was moderated in the Activity Video condition (\(\beta=1.69\), 89\% CI = {[}0.34, 2.98{]}, \emph{pd} = 0.98): shown in Figure \ref{fig:JA} (right bottom), older children did not engage in episodes of JA at a lower rate after an activity video.

@@

Four additional exploratory regressions with a similar structure were carried out to predict the number and duration of coordinated and passive JA episodes.
The regression predicting the rate of coordinated JA episodes found an effect of condition (\(\beta=0.46\), 89\% CI = {[}0.13, 0.77{]}, \emph{pd} = 0.99), with a greater rate of coordinated JA episodes occurring after the Activity Video (mean: 2.19, 95\% CI: {[}1.93, 2.46{]}) than after the Control Video (mean: 1.72, 95\% CI: {[}1.52, 1.93{]}).
There was an interaction of age and condition (\(\beta=1.59\), 89\% CI = {[}0.35, 2.94{]}, \emph{pd} = 0.98), shown in Figure \ref{fig:e2ja-coord}, revealing that after an Activity Video older children participated in coordinated JA episodes at a greater rate than children in the Control Video condition.
The regression predicting the time spent in coordinated JA episodes found no notable effects.
Older children both engaged in episodes of passive JA at a greater rate with their caregiver (\(\beta=-0.89\), 89\% CI = {[}-1.54, -0.2{]}, \emph{pd} = 0.98), and spent more time in passive JA with their caregiver (\(\beta=-5.92\), 89\% CI = {[}-9.85, -1.83{]}, \emph{pd} = 0.99).
Overall, these results show that the older children in our sample engage in more and longer episodes of joint attention with their caregivers, and that activity videos in particular lead to more episodes of coordinated JA.

As for Experiment 1, we conducted a corpus characteristic analysis to examine differences parents' language use in the two conditions.
The words that were strongly indicative of being from the Activity Video condition include \enquote{big}, \enquote{little}, \enquote{give}, \enquote{small}, \enquote{cow}, \enquote{yellow}, \enquote{take}, and \enquote{put}, while words that were most characteristic of the Science Video condition include \enquote{beep}, \enquote{like}, \enquote{neigh}, \enquote{uh-oh}, \enquote{say}, \enquote{for}, \enquote{does}, and \enquote{did}.

@@

This work was supported by a gift and a contract from Kinedu, Inc.~to the Language and Cognition Lab.
Thanks to Samaher Radwan and Megan Merrick for behavioral coding of the videos, and to members of the Language and Cognition Lab at Stanford for helpful discussion.
